Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2015-08-05 writeup/gz_hubble_data.tex
First paragraph of Sec 3.2

\usepackage{epsfig}
\usepackage{color,soul}
\begin{document}

@@

\begin{table}
\caption{Summary of FERENGI runs \label{ferengivalues}}
\begin{tabular}{lcccccc}
\hline\hline
$z_{\rm target}$ &  $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
\hline
0.3 & 8 & 7 & -3.0 & 56 & 4031 \\
0.5 & 6 & 4 & -1.5 & 24 & 1728 \\
0.8 & 3 & 3 & -1.0 & 9 & 648 \\
1.0 & 1 & 3 & -1.0 & 3 & 216 \\
\hline\hline
\end{tabular}
\end{table}

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7 evolutionary corrections (this last bit is indicated by the colour).

@@

\caption{Preliminary results of the FERENGI redshifting exercise. WARNING NO USER WEIGHTING.... For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs. smooth with redshift.}

@@

\end{center}
\end{figure}
%-----------------------------------------------------------------------------------------------------------------------------------
\subsubsection{Results of Zeta Approach (Mel stuff)}

@@

\begin{itemize}
\item talk about where purple and green tend to be on plot, and about how green areas are primarily ellipticals and disks with all the features washed out - can't tell them apart! hence, can't debias
\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
\item justify N>5 and spread < 0.2 (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $p_{bar}$, determine or justify why we won't debiase them  
\end{itemize}

@@

\begin{thebibliography}{}

\end{thebibliography}

>>>>

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\bibliographystyle{mn2e}

\begin{document}

@@

\begin{table}
\caption{Summary of FERENGI runs \label{ferengivalues}}
\begin{tabular}{lcccccc}
\hline\hline
$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm runs}$ & $N_{\rm total}$\\
\hline
0.3              & 8                  & 7                   & $-3.0$        & 56             & 4031 \\
0.5              & 6                  & 4                   & $-1.5$        & 24             & 1728 \\
0.8              & 3                  & 3                   & $-1.0$        &  9             &  648 \\
1.0              & 1                  & 3                   & $-1.0$        &  3             &  216 \\
\hline\hline
\end{tabular}
\end{table}

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the \ferengi{} code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure \ref{results1} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).

@@

\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING NO USER WEIGHTING.... For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs. smooth with redshift.}

@@

\end{center}
\end{figure}
%-----------------------------------------------------------------------------------------------------------------------------------

\subsection{Approach to debiasing morphological classifications}

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or those that vary by individual user. The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each. Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): one

\subsection{Results of Zeta Approach (Mel stuff)}

@@

\begin{itemize}
\item talk about where purple and green tend to be on plot, and about how green areas are primarily ellipticals and disks with all the features washed out - can't tell them apart! hence, can't debias
\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debiase them  
\end{itemize}

@@

\bibliography{kwrefs}
